An ultra-low noise, high-voltage piezo driver

### 2016-01-25 piezo.tex
Added details to low-noise stabilization section
Discussion of resistor 1/f noise

\begin{figure*}[t]
\includegraphics[width=\textwidth]{fig/DRV2700.ai}
\caption{Schematic of the high voltage stabilization.
The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration (see Fig.~\ref{Fig:DRV2700}).
A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
The $V_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_{\text{fb}}$.
The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:PiezoTransfer}). \label{Fig:PiezoCircuit}}
\end{figure*}

@@

The low-noise stabilization circuitry was added to remove output ripple and residual switching noise, however it serves a dual purpose as a low-gain, high-bandwidth modulation path to the high-voltage output.
It uses a very high slew-rate (\SI{4100}{\volt\per\micro\second}) op-amp, the LM7171, connected to the filtered ground node of the flyback converter.
At high frequencies, the output of this op-amp appears directly at the HV node through the capacitor $C_{\text{out}}$.
Below the corner set by $C_{\text{out}}$, the output of U2 adjusts the floating ground reference of the flyback converter.

After the passive filter ladder connecting the DRV2700 flyback converter the output,
%At high frequencies, this modulation appears directly at the HV node through the capacitors.
%At quasi-DC frequencies, the flyback regulator adjusts the HV node to keep

The choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system. (cite LIGO paper)

>>>>

\begin{figure*}[t]
\includegraphics[width=\textwidth]{fig/DRV2700.ai}
\caption{Schematic of the high voltage stabilization.
The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration (see Fig.~\ref{Fig:DRV2700}).
A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
The $V_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_1$.
The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:PiezoTransfer}). -- Add back in second set of shunt caps!\label{Fig:PiezoCircuit}}
\end{figure*}

@@

The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
To accomplish this task, a high slew-rate op-amp (Texas Instruments LM7171, \SI{4100}{\volt\per\micro\second}) drives the galvanically isolated ground node of the flyback converter (see U2 in Fig.~\ref{Fig:PiezoCircuit}).
This op-amp enforces the HV output voltage
\begin{align}
\text{V}_\text{HV} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{DC} -
\left(\frac{R_\text{mod}}{R_1}\right) \text{V}_\text{mod}
\end{align}
We choose $R_1, R_\text{mod} = \SI{1}{\mega\ohm}$, $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain is unity.
Depending on the application, however, other gain configurations would work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator since they derive from the same control voltage.
Ultimately, the op-amp U2 sets the operating voltage of the output, while the flyback converter regulates the high voltage difference between $\text{GND}_\text{HV}$ and the output.
Because the output of the flyback regulator is galvanically isolated, U2 is free to control the $\text{GND}_\text{HV}$ node at ``low'' voltages, which are transferred directly to the high voltage output.

%The low-noise stabilization circuitry was added to remove output ripple and residual switching noise, however it serves a dual purpose as a low-gain, high-bandwidth modulation path to the high-voltage output.
%It uses a very high slew-rate (\SI{4100}{\volt\per\micro\second}) op-amp, the LM7171, connected to the filtered ground node of the flyback converter.
%At high frequencies, the output of this op-amp appears directly at the HV node through the capacitor $C_{\text{out}}$.
%Below the corner set by $C_{\text{out}}$, the output of U2 adjusts the floating ground reference of the flyback converter.

%After the passive filter ladder connecting the DRV2700 flyback converter the output,
%At high frequencies, this modulation appears directly at the HV node through the capacitors.
%At quasi-DC frequencies, the flyback regulator adjusts the HV node to keep

The choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system, because this resistive divider is responsible for accurately sensing the high voltage output and noise contributions thus appear directly at the output.
Resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{k_B T R}$.
However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance~\cite{Clarke1974a,Voss1976a}.
The magnitude of this ``excess noise'' is highly dependent on the resistor composition, and varies from manufacturer to manufacturer.
Reference~\cite{Seifert2009a} characterized $1/f$ noise in a variety of resistors, and found that the Vishay TNPW \SI{0.1}{\percent}-series resistors showed a noise spectrum almost consistent with Johnson noise down to \SI{1}{\hertz}.
A previous iteration of this design used Panasonic ERJ-8ENF resistors (1206, \SI{1}{\percent}), and we noticed substantial low-frequency noise correlated with varying strain on the PCB.
This is consistent with the findings in~\cite{Seifert2009a}, which showed this Panasonic series to exhibit voltage noise two orders of magnitude larger than the TNPW series at \SI{1}{\hertz}.
